Shape Flow - Deformable Model without Landmarks

### 2015-03-24 contents/implementation.tex
Init

After solving the equation, $\bm{u_n}(\bm{x}), x \in \Omega$ gives a group of dense deformations that registering every decision functions in the shape sequence to reference frame e.g. $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame. Applying PCA on deformations gives dense deformable shape model.

>>>>

After solving the equation, $\bm{u_n}(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g. $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame. Applying PCA on deformations gives dense deformable shape model:
\begin{equation*}
    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
\end{equation*}

\begin{figure}[h!]
    \centering
        \includegraphics[width=0.5\textwidth]{resources/df}
    \caption{Deformation field built}
    \label{fig:deformationfield}
\end{figure}

\begin{figure}[h!]
    \centering
        \includegraphics[width=0.5\textwidth]{resources/models}
    \caption{Dense Deformable Model}
    \label{fig:models}
\end{figure}
